%=======================================================================%
%      CV - non accademico
%=======================================================================%
%  --- NON GENERATO AUTOMATICAMENTE ---
%
%   non ha senso automatizzarlo per adesso, le cose da aggiungere sono poche per ora.
%
%
%
%=======================================================================%





\documentclass[a4paper]{article}


\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[margin=1.5cm]{geometry}
% \addtolength{\topmargin}{-0.5cm}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\rhead{Antonio Michele Miti}
\lhead{Curriculum Vitae}
\lfoot{\footnotesize\href{https://github.com/MasterToninus/cv}{Generated on \today} }
\rfoot{\thepage \hspace{1pt} / \pageref{LastPage}}

%\usepackage[backend=bibtex, style=nature]{biblatex}
%\addbibresource{../data/publications.bib}

\setlength\parindent{0pt}


%barcharts
\newcommand{\crule}[3][black]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\progbar}[4][black]{\crule[#1]{#3}{#4}\crule[#1!10!white!90]{#2}{#4}}

%titles
\newcommand{\block}[1]{\hrule \vspace{0.2cm} \textbf{\Large #1} \vspace{0.2cm}}
\newcommand{\Block}[1]{\hrule \vspace{0.2cm} \textbf{\huge #1} \vspace{0.2cm}}
\newcommand{\blockNp}[1]{\newpage \textbf{\Large #1} \vspace{0.2cm}}

%longvoice
%expected: Event_Title,Type,Url, Approx_Date, Organization, Location, Country
\newcommand{\longvoice}[8]{
    \begin{tabular}{p{0.83\linewidth} p{0.17\linewidth} }
        \textbf{\href{#3}{#2: #1}} & #4 
        \\ 
        \textit{#5, #6, #7;} & {\small\emph{#8}}
    \end{tabular}
    \vspace{.5em}
    }
%voice
%expected: what, when, where, url, info
\newcommand{\voice}[5]{\href{#4}{\textbf{#1}} \hfill #2 \\ \textit{#3} \\ {\small #5} \vspace{0.2cm} \\}
\newcommand{\skill}[2]{\textbf{#1} \hfill #2 \\}
\newcommand{\skillbar}[4]{\textbf{#1} \hfill \progbar{#2}{#3}{#4} \\}
\newcommand{\txt}[1]{#1\\}




%---------- Document -----------
\begin{document}


%Header
\begin{minipage}[c]{0.6\columnwidth}
    \center{\huge \textbf{Antonio Michele Miti}}
    \\
    \flushleft{\normalsize \textit{Postdoctoral researcher in pure mathematics. Interested in functional programming, quantum algorithms, high performance computing, scientific programming and numerical simulations.}}
\end{minipage} 
\hfill
\begin{minipage}[t]{0.375\columnwidth}
    \vspace{-1.5em}
    \skill{\faPhone~ Phone}{+39~333~9825~418}
    \skill{\faEnvelope~ Mail}{\href{mailto:antoniomichele.miti@gmail.com}{antoniomichele.miti@gmail.com}}
    \skill{\faGlobe~ Website}{\href{https://dmf.unicatt.it/miti/}{https://dmf.unicatt.it/miti/}}
    \skill{\faGithub~ GitHub}{\href{https://github.com/MasterToninus}{MasterToninus}}    
\end{minipage}
%\textit{PhD in mathematics with a focus  on  differential geometry (multisymplectic) and its applications to physics.}
\vspace{-0.25em}



%Splash Page
\begin{minipage}[t]{0.6\columnwidth}

	\block{Current Position}

    	\voice{Postdoctoral fellow (CIVIS-3i)}
			{02/2024 -- Now}
			{Sapienza Universit\'a di Roma, Italy;}
			{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}       
			{Development of advanced mathematical models and scientific computing tools within a large European research consortium. Strong focus on interdisciplinary collaboration and project coordination.}

    \block{Work Experiences}

	\voice{Postdoctoral fellow (Assegno di ricerca)}
		{10/2022 -- 01/2024}
		{Universit\'a Cattolica del Sacro Cuore, Brescia, Italy;}
		{https://dipartimenti.unicatt.it/dmf-home}       
		{Research in applied geometry and mathematical physics. Mentored students and contributed to international publications.}
	\voice{Postdoctoral fellow (MPIM)}
		{10/2021 -- 09/2022}
		{Max Planck Institute for Mathematics, Bonn, Germany;}
		{https://www.mpim-bonn.mpg.de/}       
		 {Conducted research on higher structures and multisymplectic geometry. Gained experience in a highly international and competitive environment.}
        \voice{Doctoral Researcher}
    	{01/2017 -- 06/2021}
    	{KU Leuven, Belgium \\ Universit\'a Cattolica del Sacro Cuore, Brescia, Italy }
    	{https://scuoledidottorato.unicatt.it/phdschools/science-10574.html}
    	{Joint PhD program in differential geometry and its applications. Spent 27 months at each institution.
        Teaching assistant in graduate-level courses. Provided IT support for departmental computing infrastructure.}	
    \voice{Java Developer - Internship}
        {03/2016  -- 07/2016}
        {CST s.r.l, Milano, Italy}
        {https://www.csttech.it/}       
        {Formation in Java Programming language and in professional software development tools.}
    \voice{Student collaboration to SysAdmin}
        {05/2014 -- 02/2015}
        {LCM - Laboratorio di Calcolo e Multimedia, Universit\'a degli studi di Milano, Italy}
        {https://lcm.mi.infn.it/}       
        {Maintenance of the LCM computers cluster. Tutoring: installation and configuration of linux OS, computational physics courses.\vspace{-0.25cm}}
 

    \block{Education}

    
    \voice{Doctoral degree in Science: Mathematics}
        {April 2021}
        {Universit\'a Cattolica del Sacro Cuore and KU Leuven}
        {https://web.archive.org/save/http://scuoledidottorato.unicatt.it/phdschools/science-research-projects}       
        {Four years grant in the Joint International Doctoral Program in Science on the project \emph{Multi-symplectic geometry and applications to modern physics}. }
    \voice{Master degree in Theoretical Physics}
        {November 2015}
        {Universit\'a degli Studi di Milano}
        {https://fisica-lm.cdl.unimi.it/it}       
        {Theoretical Physics curriculum with emphases on: Foundations and Mathematical Methods in Physics, Geometric Mechanics, Computational Methods.}
    \voice{Bachelor degree in Physics}
        {October 2010}
        {Universit\'a degli Studi di Milano - Bicocca}
        {https://www.fisica.unimib.it/en}       
        {Theoretical Physics curriculum with emphases on: Mathematical-Physics, Classical and Quantum Mechanics.\vspace{-0.25cm}}

















\end{minipage} 
\hfill
\begin{minipage}[t]{0.375\columnwidth}
   
    \block{Bio}

	\skill{Born}{1986 in Milano, Italy}
	\skill{Citizenship}{Italian}
	\skill{Marital Status}{Married with 1 child}



    \block{Languages} 
        
    \skill{Italian}{Mothertongue}
    \skill{English}{Toefl-IBT : 102/120 (apr-18)}
    \skill{French}{Beginner}
        





    \block{Computer Skills} 
    
    
    \skillbar{C/C++}
    {1cm}
    {1cm}
    {0.25cm}
    \skillbar{Python}
    {1cm}
    {1cm}
    {0.25cm}
    \skillbar{Haskell}
    {1.5cm}
    {0.5cm}
    {0.25cm}
    \skillbar{Cuda}
    {.75cm}
    {1.25cm}
    {0.25cm}
    \skillbar{Java}
    {.75cm}
    {1.25cm}
    {0.25cm}
    \skillbar{Mathematica}
    {1.5cm}
    {0.5cm}
    {0.25cm}
    \skillbar{\LaTeX}
    {0cm}
    {2cm}
    {0.25cm}
    \skillbar{Linux (Sysadmin)}
    {0.5cm}
    {1.5cm}
    {0.25cm}
    \skillbar{Windows (Sysadmin)}
    {0.5cm}
    {1.5cm}
    {0.25cm}
    \skillbar{Embedded electronics}
    {1.5cm}
    {0.5cm}
    {0.25cm}
    \skillbar{Computer assembly}
    {1.0cm}
    {1.0cm}
    {0.25cm}
    \skillbar{Network infrastructure}
    {1.5cm}
    {0.5cm}
    {0.25cm}


    \block{Academic Track}

    \skill{Scientific Pubblications}{8 }
    \skill{Courses Taught}{6 (50+ hours) }
    \skill{Conference Talks}{20+ }
    \skill{Conference Organized}{3 }
    \skill{Research Stays Abroad}{10+ }
    \skill{Research Grants Won}{15} %phd brescia, minho, udine, napoli. postdoc stpeter, varsavia,bonn,brescia, roma, unimib. indam: 4 viaggi, 1 mensilità estero

\block{Honors \& Awards}

\voice{French Habilitation to Assistant Professor }
  {02/2022}
  {Minist\'ere français de l'Enseignement sup\'erieur et de la Recherche}
  {https://www.galaxie.enseignementsup-recherche.gouv.fr/ensup/qualification/Resultats_2022/qualifies_MCF_2022.pdf}
  {National qualification in pure mathematics for university-level teaching and research positions. (Maitre de conf\'erences, Section 25)}
\voice{Research Abroad Grant}
  {05/2023}
  {Istituto Nazionale di Alta Matematica}
  {https://www.altamatematica.it/wp-content/uploads/2022/12/bando-estero-2022-2023-1.pdf}
  {Competitive research grant (€3,000) supporting an international research stay.}
\voice{Merit Award}
  {12/2015}
  {BCC di Carugate e Inzago, Italy}
  {https://web.archive.org/web/20191207203437/https://www.bccmilano.it/news/dettaglio_news_div.asp?i_menuID=54872&hNewsID=132411}
  {Award and monetary prize for outstanding academic performance at graduation.}



\end{minipage}


\clearpage

    \block{Technical Training}
   
    \longvoice{Functional Programming and Domain-Specific Languages}
        {Industry Course}
        {https://dtai.cs.kuleuven.be/events/fpcourse/}
        {October 2019}
        {KU Leuven}
        {Leuven}
        {Belgium}
        {}
    \longvoice{Scientific computing with Python}
        {PhD Course}
        {https://web.archive.org/web/20180604081514/http://dmf.unicatt.it/~della/pythoncourse18/}
        {June 2018}
        {Universit\'a Cattolica del Sacro Cuore}
        {Brescia}
        {Italy}
        {}
    \longvoice{Computational methods for the solution of Differential Equations}
        {PhD Course}
        {https://www.dropbox.com/s/q2rapau2k49n5t7/1802-Course-NumericalPdeAvella.pdf?dl=0}
        {February 2018}
        {Universit\'a Cattolica del Sacro Cuore}
        {Brescia}
        {Italy}
        {}
    \longvoice{Python for computational science}
        {Training Course}
        {https://web.archive.org/web/20170623170252/https://eventi.cineca.it/en/hpc/python-computational-science}
        {February 2017}
        {CINECA-SCAI}
        {Milan}
        {Italy}
        {}
    \longvoice{Introduction to Scientific and Technical Computing in C++}
        {Training Course}
        {https://web.archive.org/save/http://www.hpc.cineca.it/content/introduction-object-oriented}
        {March 2016}
        {CINECA-SCAI}
        {Milan}
        {Italy}
        {}
    \longvoice{B2 General English Intensive course}
        {Training Course}
        {https://www.britishcouncil.it/en/english/courses-adults/general}
        {January 2016}
        {British Council Milano}
        {Milan}
        {Italy}
        {}
    \longvoice{Introduction to Scientific Programming using GPGPU and CUDA}
        {Training Course}
        {https://web.archive.org/web/20170623171128/http://www.hpc.cineca.it/content/introduction-to-gpu}
        {March 2014}
        {CINECA-SCAI}
        {Milan}
        {Italy}
        {}
    









\end{document}