\documentclass[a4paper]{article}


\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.5cm]{geometry}
% \addtolength{\topmargin}{-0.5cm}
\usepackage{xcolor}

\usepackage[backend=bibtex, style=nature]{biblatex}
\addbibresource{../biblio.bib}

\setlength\parindent{0pt}
\pagenumbering{gobble}

%barcharts
\newcommand{\crule}[3][black]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\progbar}[4][black]{\crule[#1!10!white!90]{#2}{#4}\crule[#1]{#3}{#4}}

%titles
\newcommand{\block}[1]{\hrule \vspace{0.2cm} \textbf{\Large #1} \vspace{0.2cm}}
\newcommand{\Block}[1]{\hrule \vspace{0.2cm} \textbf{\huge #1} \vspace{0.2cm}}

%voices
\newcommand{\voice}[4]{\textbf{#1} \hfill #2 \\ \textit{#3} \\ {\small #4} \vspace{0.2cm} \\}
\newcommand{\skill}[2]{\textbf{#1} \hfill #2 \\}
\newcommand{\skillbar}[4]{\textbf{#1} \hfill \progbar{#2}{#3}{#4} \\}
\newcommand{\txt}[1]{#1\\}

\begin{document}
\begin{minipage}[t]{0.6\columnwidth}
    

    \block{Education}

    
    \voice{Phd Student in Statistical Mechanics}
        {10/2018 -- present}
        {Universit\'a degli Studi di Milano}
        {Supervisor: Sergio Caracciolo\\ Research topics: Combinatorial Optimization, Theoretical Data Science}
    \voice{University Student in Physics}
        {10/2013 -- 10/2018}
        {Universit\'a degli Studi di Milano}
        {3 years of Physics (final grade 110/110 cum laude, supervisor Prof.~Luca Molinari)\\+ 2 years of Theoretical Physics (final grade 110/110 cum laude, supervisor Prof.~Sergio Caracciolo)}



    \block{Schools}

    
    \voice{Winter School}
        {02/2019}
        {Galileo Galilei Institute, Florence (IT)}
        {Lectures about Statistical Field Theory in Condensed Matter.}
    \voice{Summer School}
        {09/2015}
        {European Syncrothron Radiation Facility, Grenoble (FR)}
        {Lectures about x-ray and neutron techniques in diffractometry and spectroscopy. Experimental project (Fluorescence Spectroscopy of Eu3+) with the "Electronic structure, magnetism and dynamics" group.}
    \voice{Internship}
        {02/2013}
        {European Joint Research Center, Ispra (IT)}
        {Activities with researchers on: nuclear decomissioning, radioprotection and EU community policies.}
    \voice{Summer School}
        {06/2012}
        {Scuola Normale Superiore, Pisa (IT)}
        {Lectures by experts on a wide variety of topics, from Literature to Physics.}



    \block{Work}

    
    \voice{University Tutor}
        {03/2019 -- 09/2019}
        {Universit\'a degli Studi di Milano}
        {Tutoring for Complex and Functional Analysis course.}
    \voice{Supervisor for Junior Camps}
        {09/2014 -- 12/2017}
        {Sardinia Radio Telescope, Cagliari (IT) \& Nus Observatory, Nus (IT)}
        {Logistic and teaching support at 6 different Astrophysics Junior Camps organized by Sterrenlab.}
    \voice{Physics Teacher}
        {10/2016 -- 06/2017}
        {Istituto Professionale "L. Einaudi", Varese (IT)}
        {Physics teacher for the first year adult class of a professional secondary public school.}
    \voice{Private Lecturer}
        {11/2013 -- 06/2018}
        {Varese (IT)}
        {Private lectures in Maths and Physics up to universiatry education. Private lectures in Computer Science, Chemistry and Latin up to high school education.}


\end{minipage} 
\hfill
\begin{minipage}[t]{0.375\columnwidth}
    
    \Block{\hfill Vittorio Erba\hfill}

    \skill{Phone}{+39~345~236~0130}
    \skill{Mail}{erba.vittorio@gmail.com}
    \skill{Site}{vittorioerba.github.com}

    

    \block{Languages} 
    
    
    \skill{Italian}{Mothetongue}
    \skill{English}{Certified CEFR C1}
        



    \block{Computer Skills} 
    
    
    \skillbar{C++}
    {0.8999999999999999cm}
    {1.1cm}
    {0.25cm}
    \skillbar{Python}
    {1.0cm}
    {1.0cm}
    {0.25cm}
    \skillbar{Julia}
    {1.5cm}
    {0.5cm}
    {0.25cm}
    \skillbar{Mathematica}
    {0.7cm}
    {1.3cm}
    {0.25cm}
    \skillbar{Bash}
    {1.3cm}
    {0.7cm}
    {0.25cm}
    \skillbar{\LaTeX}
    {0.5cm}
    {1.5cm}
    {0.25cm}
    \skillbar{Office suites}
    {0.5cm}
    {1.5cm}
    {0.25cm}
    \skillbar{HTML, CSS}
    {1.2cm}
    {0.8cm}
    {0.25cm}



    \block{Honors \& Awards}

    
    \voice{Excellence Scholarship}
        {2015 -- 2017}
        {Università degli Studi di Milano}
        {\vspace{-0.5cm}}
    \voice{1st place "Valerio Filippini"}
        {04/2012}
        {University of Pavia (IT)}
        {Contest in Physics for high school students.}
    \voice{Guitar Studies Scholarship}
        {2005 \& 2012}
        {Municipality of Besozzo (IT)}
        {\vspace{-0.5cm}}
    \voice{Diplom in Solfege}
        {06/2008}
        {Conservatory of Novara (IT)}
        {\vspace{-0.5cm}}



    \block{Volunteering}

    
    \voice{Migrant hosting facilities}
        {2017}
        {Laveno (IT)}
        {\vspace{-0.5cm}}
    \voice{Secretary of AISF}
        {2015 -- 2017}
        {AISF: Italian Association of Physics Students}
        {\vspace{-0.5cm}}
    \voice{PAPAP16 Organizer}
        {2016}
        {PAPAP: Particle and Astroparticle Physics Autumn Programme}
        {Full organization of the visits to the Frascati INFN Labs and to the Gran Sasso LNGS Labs.}


\end{minipage}

\block{Selected publications}

\nocite{*}
\printbibliography[heading=none]

\end{document}